\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}




%by: Aline R. Antunes

\begin{document}
\begin{center}
    \textbf{Manaal Faruqui}\\ 
    \hrulefill
\end{center}

\begin{center}
    Research Scientist \textbullet \ Meta \textbullet \ manaalfar@gmail.com \textbullet \ +1 479-430-6664
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Experience}
\end{center}

\textbf{Meta Superintelligence Labs} \hfill New York City

\textbf{Research Scientist} \hfill Jan 2025 - present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Model capability lead of all text workstreams for post-training (working with 30+ engineers)
    \item Worked on evaluations, data collection and model-training for post-training (response gen. + tool-calling)
    \item Setup process to understand and improve user engagement in Meta AI in apps like Whatsapp
   
\end{itemize}

\vspace{12pt}

\textbf{Google Gemini} \hfill New York City

\textbf{Senior Staff Research Scientist, Manager} \hfill 2023 - 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Co-lead of the core modeling team; managing a team of 14 software engineers and research scientists.
    \item Working on producing high quality post-training finetuning data for Gemini across workstreams.
    \item Overall lead of the instruction following, and reasoning pillars; Tech-lead of factuality, and safety pillars.
    \item Post-training recipe optimization, and evaluation.
\end{itemize}

\vspace{12pt}

\textbf{Google Assistant} \hfill New York City

\textbf{Staff Research Scientist, Manager} \hfill 2021 - 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Managed a team of 5 software engineers and research scientists.
    \item Made interactions with Assistant more natural wherein the users and assistant can interrupt each other.
    \item Launched the best NLU models on TPU chips in Pixel phones.
\end{itemize}

\vspace{12pt}

\textbf{Google Assistant} \hfill New York City

\textbf{Senior Research Scientist} \hfill 2018 - 2021
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Brought speech signals from ASR to NLU for end to end optimization of losses for Google Assistant
    \item Improved NLU for noisy user queries including disfluencies.
\end{itemize}

\vspace{12pt}

\textbf{Google Research} \hfill New York City

\textbf{Research Scientist} \hfill 2016 - 2018
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Worked on understanding language structure through edits made by users on Wikipedia.
    \item Improved the quality of ``People also ask'' questions on Google search.
\end{itemize}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{Carnegie Mellon University} \hfill Pittsburgh, PA

PhD, Computer Science. \hfill 2012 - 2016\\
Thesis: \href{https://www.manaalfaruqui.com/papers/thesis.pdf}{Diverse Context for Learning Word Representations}

\vspace{12pt}

\textbf{Indian Institute of Technology Kharagpur} \hfill Kharagpur, India\\
B.Tech \& M.Tech (Hons.) in Computer Science \hfill	2007 - 2012

\vspace{12pt}

\begin{center}
    \textbf{Relevant Information}
\end{center}

\textbf{Publications:}
My most recent publications and patents can be found on \href{https://scholar.google.com/citations?hl=en&user=W-CxZCgAAAAJ}{Google Scholar}.\\
\textbf{Book:} \href{https://www.morganclaypool.com/doi/abs/10.2200/S00920ED2V01Y201904HLT042}{Cross-Lingual Word Embeddings}, Synthesis Lectures on HLT, Morgan \& Claypool Publishers, 2019.\\
\textbf{Awards:}
\href{https://naacl.org/naacl-hlt-2015/best-paper-awards.html}{Best Paper Award at NAACL 2015} for \href{https://arxiv.org/abs/1411.4166}{Retrofitting Word Vectors to Semantic Lexicons}.\\
\textbf{Service:} Senior Area Chair and Area Chair at ACL, ICLR, EACL, NAACL, EMNLP through the years.\\




\end{document}
